On finiteness of structures produced deterministically by co-transcriptional folding

### 2018-11-14 ttt.tex
11/14 before dinner

Let us consider the stabilization of the $i$-th bead $a_i$ upon $C_{i-1}$. The bead cannot collaborate with any succeeding bead $w[i+1],w[i+2],\cdots$ at delay 1. There are just two ways to get stabilized at delay 1. One way is to be bound to another bead. The other way is through a $tunnel\ section$. A tunnel section consists of four beads that occupy four neighbors of a point (Fig.\ref{TTT_tunnel_intro}). 
How they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section. 
Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free. We call such a bead $p$ as $inside\ of\ a\ tunnel$ and such beads $p^\prime$ as $entrance\ of\ a\ tunnel$ without a case that $p^\prime$ is inside of a tunnel. If the beads $w[i-2]$ and $w[i-1]$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $w[i]$ cannot help but be stabilized at the other free neighbor. In this way, $w[i]$ can get stabilized without being bound.

@@

\begin{theorem}[Tunnel Troll Theorem]
  Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha \geq 2$. If there is a part of transcript $w[i-1..j+1] = btt...tb$, then $C_i$'s binding capabilities is more than $C_j$'s binding capabilities.
\end{theorem}

\subsection{Proof of Tunnel Troll Theorem}
Assume $\Xi$ is deterministic. %How they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section. 
Each of beads in transcript are bound either inside of tunnel or outside (Fig. \ref{TTT_position1}). If a bead is stabilized at inside of tunnel, then its successor is already decided the position either inside of a tunnel or outside. Moreover, If a bead is stabilized at outside of a tunnel, then its position is an entrance of a tunnel or otherwise.

Tunnel sections have three possible shape with considering symmetry such as straight, acute turn and obtuse turn (Fig. \ref{TTT_tunnel}). Let us focus entrances of a tunnel such as $p^\prime$, then Entrances have two possible shape (Fig. \ref{TTT_enterpoint}).

Let us consider tunnel sections only tunnel A and B. See Fig. \ref{TTT_position2}. From appendix (Entrance of Tunnel A, B and Exit of Tunnel), we add maximum number which each transitions provide binding capabilities for each edge where $a$ is number of consuming binding capabilities when the bead is stabilized at position of $successer\ in\ outside$.

Next, we consider on tunnel C section. If $w[i]$ is stabilized by tunnel C and $S[i+1]$ is $t$, then $w[i+1]$ is stabilized by tunnel A or B because if $w[i+1]$ is stabilized by tunnel C, then $C_{i+1}$ is a terminal. Hence, tunnel C section is devided cases sush as Figure \ref{TTT_tunnelC_graph}. Cases of $S[i...] = bt^l (l \geq 2)$ are already considered (Upper). According to appendix (Tunnel C), cases of $S[i..i+2] = btb$ also consume some binding capabilities (Lower).

@@

    \end{tabular}
    \caption{All possible tunnel sections}
    \label{TTT_tunnel}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}

      \begin{minipage}{0.2\hsize}
      \centering
        \begin{tikzpicture}

          \begin{scope}[xshift=1cm, yshift=2cm]
            \fill(0,0) circle [radius=0.1];
            \node[above] at (180:1.2) {$p^\prime$};

            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];

            \foreach \theta in {120,-120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

            \draw[->] (-1.1,0) -- (-0.1,0);
          \end{scope}

          \node at (0.25,0) {Tunnel A,B};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.2\hsize}
      \centering
        \begin{tikzpicture}

          \begin{scope}[xshift=1cm, yshift=2cm]
            \fill(0,0) circle [radius=0.1];
            \node[above] at (180:1.2) {$p^\prime$};

            \draw[transform canvas={shift=(-120:1.2)}](0,0) circle [radius=0.1];
            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];

            \foreach \theta in {120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

            \draw[->] (-1.1,0) -- (-0.1,0);
          \end{scope}

          \node at (0.25,0) {Tunnel C};
        \end{tikzpicture}
      \end{minipage}

    \end{tabular}
    \caption{Entrance of a tunnel}
    \label{TTT_enterpoint}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \draw[thick]
      (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
      \node at(2.5,1) {Outside};
      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {Entrance of a tunnel};
      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {Otherwise};

      \draw[thick]
      (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
      \node at(10.5,1) {Inside of a tunnel};
      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};

      \draw[->]
      (outside) edge [bend left] node[left] {$b$} (enter)
                edge [loop left] node[left] {$b$} (outside)
      (enter)   edge [bend left] node[above] {$b$} (next-tunnel)
                edge [bend left] node[above] {$b$} (next-outside)
                edge [bend left] node[right] {$b$}  (outside)
      (next-tunnel) edge         node[right] {$t$} (next-outside)
                edge [loop right]node[below] {$t$}    (next-tunnel)
      (next-outside) edge[bend left] node[above] {$t$}  (outside)
                edge [bend left]     node[above] {$t$}(enter)
      ;

    \end{tikzpicture}
    \caption{Cases on position of a bead}
    \label{TTT_position1}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \draw[thick]
      (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
      \node at(2.5,1) {Outside};
      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {Entrance of a tunnel};
      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {Otherwise};

      \draw[thick]
      (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
      \node at(10.5,1) {Inside of a tunnel};
      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Successer in inside};
      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Successer in outside};

      \draw[->]
      (outside) edge [bend left] node[left] {$-1$} (enter)
                edge [loop left] node[left] {$\pm 0$} (outside)
      (enter)   edge [bend left] node[above] {$-1$} (next-tunnel)
                edge [bend left] node[above] {$-a$} (next-outside)
                edge [bend left] node[right] {$\pm 0$}  (outside)
      (next-tunnel) edge         node[right] {$-a$} (next-outside)
                edge [loop right]node[below] {$\pm 0$}    (next-tunnel)
      (next-outside) edge[bend left] node[above] {$+a$}  (outside)
                edge [bend left]     node[above] {$+(a-1)$}(enter)
      ;

    \end{tikzpicture}
    \caption{Increment on Tunnel A,B}
    \label{TTT_position2}
  \end{center}
\end{figure}

@@

@@

\begin{itemize}
\item{Case of $t_0$}\\
  Let us consider points of $c,d$ either occupied or not. A point $c$ or $d$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel. If $c$ is free, then $p^\prime$ has to be bound to a bead except $A$ due to deterministically stabilize. In this situation, at least three neighbors of A are free that is at most three neighbors of A are occupied. A leave at least one binging capability because beads of beighbors are predecessor and successor in addition A is able to consume itself binging capabilities only one-time. Hence, $p^\prime$ must be bound to A. Thus, a case of $t_0$ consumes some binding capabilities.

\item{Case of $t_{\pm 60}$}\\
  In this case, a point $c$ or $d$ is free, too. If $c$ is free, $p^\prime$ has to be bound to A or B. If $c$ is occupied, then $d$ is free. This time, B has some binding capabilitie so $p^\prime$ has to be bound to B.

  In this situation, $p^\prime$ is able to supply a binding capability. if this capability is active, $p^\prime$ bind a bead into $c$ or $d$. However, B and P are exist in back bone. According to Jordan curve theorem, any successors of $p^\prime$ cannot reach a point $c$ or $d$ so this capability is inactive. Thus, a case of $t_{\pm 60}$ consumes some binding capabilities.

\item{Case of $t_{\pm 120}$}\\
  Binding capabilities that $p^\prime$ supply are inactive according to Jordan curve theorem on A and P. Moreover, $p^\prime$ has to be bound to one of $c$, $d$,$e$ in order to deterministically stabilize.
Thus, a case of $t_{\pm 120}$ consumes some binging capabilities.

@@

            \node[transform canvas={shift=(60:1.2)},right] {A};
            \node[transform canvas={shift=(-60:1.2)},right] {B};
            \node[transform canvas={shift=(120:1.2)},left] {c};
            \node[transform canvas={shift=(-120:1.2)},left] {d};

@@

            \node[transform canvas={shift=(60:1.2)},right] {A};
            \node[transform canvas={shift=(-60:1.2)},right] {B};
            \node[transform canvas={shift=(120:1.2)},left] {P};

            \node[transform canvas={shift=(180:1.2)},left] {c};
            \node[transform canvas={shift=(-120:1.2)},left] {d};

@@

            \node[transform canvas={shift=(-60:1.2)},right] {A};
            \node[transform canvas={shift=(60:1.2)},right] {P};

            \node[transform canvas={shift=(120:1.2)},left] {c};
            \node[transform canvas={shift=(180:1.2)},left] {d};
            \node[transform canvas={shift=(-120:1.2)},left] {e};
            \node[transform canvas={shift=(0:1.2)},below] {n};

@@

Fig.\ref{TTT_tunnel_exit} exhibits all the two kings of exit of tunnel. 
At least one of point $c$ or $d$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.

@@

\begin{itemize}
\item{Case of $c$ and $d$ are free}\\
  This case can be regarded same situation as entrance. See Fig.\ref{TTT_tunnel_exit} (Left). Predecessor P has to be bound A and B because each of A and B leave binding capabilities. Hence, at least $a=2$. This time, $\alpha = 2$ that is this case supply at most only $a$ binding capabilities.

\item{Case of $c$ is occupied}\\
  See Fig.\ref{TTT_tunnel_exit} (Right). If $c$ is pccupied, then $d$ is free so that P has to be bound B. Hence, at least $a=1$. This case can supply two binding capabilities but $p^\prime$ can bind to only one of $e$ or $d$ because $e$ or $d$ will be occupied a successor of $p^\prime$. Therefore, this case supply at most only $a=1$ active binding capabiliry.

@@

\begin{itemize}
\item{Case of $c$ and $d$ are free}\\
  In $\alpha \geq 3$, if three neighbors of a bead leave, then it can supply two binding capabilities. Therefore Predecessor P has to be bound A and B, and $p^\prime$, too. In this case, at least consumes four bindings and supplies at most two bindings. Thus, it consumes some binding capabilities, totally.

\item{Case of $c$ is occupied}\\
  In this case, B leave at least two bindings and A, $c$ also leave at least one binding. Therefore P has to be bound A and B, and $p^\prime$ also has to be bound B and $c$. In this case, at least consumes four bindings and supplies at most one binding. Thus, it consumes some binding capabiliries, totally.
\end{itemize}

@@

            \node[transform canvas={shift=(120:1.2)},right] {A};
            \node[transform canvas={shift=(-120:1.2)},right] {B};
            \node[transform canvas={shift=(180:1.2)},left] {P};

            \node[transform canvas={shift=(60:1.2)},left] {c};
            \node[transform canvas={shift=(-60:1.2)},left] {d};

          \node at (0,-2) {Point $c$ and $d$ are free};
        \end{tikzpicture}
      \end{minipage}

@@

            \node[transform canvas={shift=(120:1.2)},right] {A};
            \node[transform canvas={shift=(-120:1.2)},right] {B};
            \node[transform canvas={shift=(180:1.2)},left] {P};

            \node[transform canvas={shift=(-60:1.2)},right] {d};
            \node[transform canvas={shift=(60:1.2)},right] {c};
            \node[transform canvas={shift=(0:1.2)},right] {e};

          \node at (0,-2) {Point $c$ is occupied};
        \end{tikzpicture}
      \end{minipage}

@@

\begin{itemize}
\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
  In this figure, Bead A has at least one binding so that $w_{i-2}$ has to bound A. Moreover, $w_{i-1}$ has to bound one of B, C, D in order to stabilize deterministically. On the other hand, $w_i$ can supply two bindings but free neighbors of $w_i$ are two points. One of them is occupied a successor. Therefore $w_i$ can only bind one of $e,f$ that is $w_i$ supplies at most one binding. Thus, this case consumes some binding capabilities.

\item{Right of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
  This cases are divided on number of capabilities that $w_{i-2}$ consumes.
  \begin{itemize}
  \item[-]{$w_i$ does not consume any bindings}\\
    $w_{i-1}$ has to bound one of B, C, D in order to stabilize deterministically. $w_i$ has to be bound to $w_{i-2}$ because $w_{i-2}$ has bindings. This time, let us consider either $e$ is occupied or not. If $e$ is occupied, then $w_{i-2}$ has no active bindings that is this situation consumes some binding capabilities. If $e$ is free and $w_{i+1}$ is stabilized in $e$, then $w_{i-2}$ has to bind $w_{i+1}$. Therefore, In this case, stabilization of $w[i-2..i+1]$ consumes some bindings. If $e$ is free and $w_{i+1}$ is stabilized except $e$, then this oritatami system has to use two binding capabilities in order to bind $w_{i+1}$. Therefore, in this case consumes some bindings. Thus in this cases consume some binding capabilities.

  \item[-]{$w_i$ consumes one binding}\\
    In this case, $w_{i-1}$ has to be bound one of B, C, D. In addition, $w_{i-2}$ and $w_i$ are not supply any bindings. Thus, in this cases consume some binding capabilities.。
  \item[-]{$w_i$ consumes two bindings}\\
    In this case, $w_{i-2}$ already consumes two binding. $w_{i-1}$ has to be bound. $w_i$ supplies two bindings. Thus, in this cases consume some binding capabilities.

@@

          \node[left] at (-60:1.2) {A};

@@

            \foreach \theta in {120,60,-60}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

@@

            \node[below] at (180:1.2) {$w_{i-2}$};
            \node[right] at (0:0) {$w_{i-1}$};
            \node[right] at (-120:1.2) {$w_i$};

            \node[left] at (120:1.2) {B};
            \node[left] at (60:1.2) {C};
            \node[left] at (0:1.2) {D};

@@

              \node[right] at (-120:1.2) {e};
              \node[right] at (-60:1.2) {f};
            \end{scope}

@@

            \node[below] at (180:1.2) {$w_{i-2}$};
            \node[right] at (0:0) {$w_{i-1}$};
            \node[right] at (-120:1.2) {$w_i$};

>>>>

Let us consider the stabilization of the $i$-th bead $a_i$ upon $C_{i-1}$. The bead cannot collaborate with any succeeding bead $w[i+1],w[i+2],\cdots$ at delay 1. There are just two ways to get stabilized at delay 1. One way is to be bound to another bead. The other way is through a $tunnel\ section$. A tunnel section consists of four beads that occupy four neighbors of a point (Fig.\ref{TTT_tunnel_intro}). 
Accordingly, how they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.

Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free. We call such a bead $p$ as $inside\ of\ a\ tunnel$ and such beads $p^\prime$ as $entrance\ of\ a\ tunnel$ without a case that $p^\prime$ is inside of a tunnel. If the beads $w[i-2]$ and $w[i-1]$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $w[i]$ cannot help but be stabilized at the other free neighbor. In this way, $w[i]$ can get stabilized without being bound.

@@

\begin{theorem}[Tunnel Troll Theorem]
  Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha \geq 2$. If there is a part of transcript $w[i..j+1] = bttt...tb$, then $C_i$'s binding capabilities is more than $C_j$'s binding capabilities.
\end{theorem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Proof of Tunnel Troll Theorem}
Assume $\Xi$ is deterministic. %How they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section. 
Each of beads in transcript are bound either inside of tunnel or outside (Fig. \ref{TTT_position}). If a bead is stabilized at inside of tunnel, then its successor is already decided the position either inside of a tunnel or outside. Moreover, If a bead is stabilized at outside of a tunnel, then its position is an entrance of a tunnel or otherwise.

Tunnel sections have three possible shape with considering symmetry such as straight, acute turn and obtuse turn (Fig. \ref{TTT_tunnel}). %Let us focus entrances of a tunnel such as $p^\prime$, then Entrances have two possible shape (Fig. \ref{TTT_enterpoint}).

Let us consider each of cases of tunnel A, B, and C. Accordingly, We use lemma \ref{TTT_neighbor_lemma}

\begin{lemma}
\label{TTT_neighbor_lemma}
If a bead does not have any bond, then neighbors of it must be occupied by $\alpha + 2$ beads at $\delta = 1$ and unary except first and last beads.
\end{lemma}

A bead in transcript needs predecessor and successor except first and last beads. If the bead does not have ant bond, then it use hand with $\alpha$ neighbors. Thus, lemma \ref{TTT_neighbor_lemma} is clearly true.

\paragraph{}
Let us consider tunnel sections only tunnel A and B. See Fig. \ref{TTT_position}. From appendix (Entrance of Tunnel A, B and Exit of Tunnel), we add maximum number which each transitions provide binding capabilities for each edge where $a$ is number of consuming binding capabilities when the bead is stabilized at position of $successor\ in\ outside$.

%The sequence $S$ can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+ \cup bt^+bt^+$.

Next, we consider on tunnel C section. If $w[i]$ is stabilized by tunnel C and $S[i+1]$ is $t$, then $w[i+1]$ is stabilized by tunnel A or B because if $w[i+1]$ is stabilized by tunnel C, then $C_{i+1}$ is a terminal. Hence, tunnel C section is divided cases such as Figure \ref{TTT_tunnelC_graph}. Cases of $S[i...] = bt^l (l \geq 2)$ are already considered (Upper). According to appendix (Tunnel C), cases of $S[i..i+2] = btb$ also consume some binding capabilities (Lower).

@@

    \end{tabular}
    \caption{All possible tunnel sections: straight, acute turn, and obtuse turn}
    \label{TTT_tunnel}
  \end{center}
\end{figure}

%\begin{figure}
%  \begin{center}
%    \begin{tabular}{cc}
%      
%      \begin{minipage}{0.2\hsize}
%      \centering
%        \begin{tikzpicture}
%
%          \begin{scope}[xshift=1cm, yshift=2cm]
%            \fill(0,0) circle [radius=0.1];
%            \node[above] at (180:1.2) {$p^\prime$};
%            
%            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
%            
%            
%            \foreach \theta in {120,-120}{
%              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
%              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
%            }
%
%            \draw[->] (-1.1,0) -- (-0.1,0);
%          \end{scope}
%
%          \node at (0.25,0) {Tunnel A,B};
%        \end{tikzpicture}
%      \end{minipage}
%
%      \begin{minipage}{0.2\hsize}
%      \centering
%        \begin{tikzpicture}
%
%          \begin{scope}[xshift=1cm, yshift=2cm]
%            \fill(0,0) circle [radius=0.1];
%            \node[above] at (180:1.2) {$p^\prime$};
%
%            \draw[transform canvas={shift=(-120:1.2)}](0,0) circle [radius=0.1];
%            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
%            
%            
%            \foreach \theta in {120}{
%              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
%              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
%            }
%
%            \draw[->] (-1.1,0) -- (-0.1,0);
%          \end{scope}
%
%          \node at (0.25,0) {Tunnel C};
%        \end{tikzpicture}
%      \end{minipage}
%
%    \end{tabular}
%    \caption{Entrance of a tunnel}
%    \label{TTT_enterpoint}
%  \end{center}
%\end{figure}

%\begin{figure}
%  \begin{center}
%    \begin{tikzpicture}
%      \draw[thick]
%      (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
%      \node at(2.5,1) {Outside};
%      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {Entrance of a tunnel};
%      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {Otherwise};
%
%      
%      
%      \draw[thick]
%      (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
%      \node at(10.5,1) {Inside of a tunnel};
%      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
%      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
%
%      \draw[->]
%      (outside) edge [bend left] node[left] {$b$} (enter)
%                edge [loop left] node[left] {$b$} (outside)
%      (enter)   edge [bend left] node[above] {$b$} (next-tunnel)
%                edge [bend left] node[above] {$b$} (next-outside)
%                edge [bend left] node[right] {$b$}  (outside)
%      (next-tunnel) edge         node[right] {$t$} (next-outside)
%                edge [loop right]node[below] {$t$}    (next-tunnel)
%      (next-outside) edge[bend left] node[above] {$t$}  (outside)
%                edge [bend left]     node[above] {$t$}(enter)
%      ;
%      
%    \end{tikzpicture}
%    \caption{Cases on position of a bead}
%    \label{TTT_position1}
%  \end{center}
%\end{figure}

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \draw[thick, gray]
      (0.5,1)--(0,1)--(0,4)--(4,4)--(4,1)--(3.5,1);
      \node at(2,1) {Outside};
      \node at (2,3.2) [rectangle, draw, rounded corners] (enter) {Entrance of a tunnel};
      \node at(2,1.8) [rectangle, draw, rounded corners] (outside) {Otherwise};

      \draw[thick, gray]
      (7.5,1)--(7,1)--(7,4)--(11,4)--(11,1)--(10.5,1);
      \node at(9,1) {Inside of a tunnel};
      \node at(9,3.2) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
      \node at(9,1.8) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};

      \draw[->]
      (outside) edge [bend left, blue] node[left] {$s=b,\Delta=-1$} (enter)
                   edge [loop left, blue] node[below left] {$s=b,\Delta=\pm 0$} (outside)
      (enter)   edge [bend left, blue] node[above] {$s=b,\Delta=-1$} (next-tunnel)
                edge [bend left, blue] node[above] {$s=b,\Delta=-a$} (next-outside)
                edge [bend left, blue] node[right] {$s=b,\Delta=\pm 0$}  (outside)
      (next-tunnel) edge[teal]         node[right] {$s=t,\Delta=-a$} (next-outside)
                edge [loop right, teal]node[right] {$s=t,\Delta=\pm 0$}    (next-tunnel)
      (next-outside) edge[bend left, teal] node[above] {$s=t,\Delta=+a$}  (outside)
                edge [bend left, teal]     node[above] {$s=t,\Delta=+(a-1)$}(enter)
      ;

    \end{tikzpicture}
    \caption{Increment on Tunnel A,B}
    \label{TTT_position}
  \end{center}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%/////////////////////////////////////////////////
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{itemize}
\item{Case of $t_0$}\\
  Let us consider points of $n_3,n_4$ either occupied or not. A point $n_3$ or $n_4$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel. If $n_3$ is free, then $p^\prime$ has to be bound to a bead except $n_1$ due to deterministically stabilize. In this situation, at least three neighbors of $n_1$ are free that is $n_1$ leave at least one bond from lemma \ref{TTT_neighbor_lemma}. Hence, $p^\prime$ must be bound to $n_1$. Thus, a case of $t_0$ consumes two binding capabilities and it does not supply any binding capabilities.

\item{Case of $t_{\pm 60}$}\\
  In this case, a point $n_4$ or $n_5$ is free, too. If $n_5$ is free, $p^\prime$ has to be bound to $n_1$ or $n_2$. If $n_5$ is occupied, then $n_4$ is free. This time, $n_2$ has some binding capabilities so $p^\prime$ has to be bound to $n_2$.

  In this situation, $p^\prime$ is able to supply a binding capability. if this capability is active, $p^\prime$ bind a bead into $n_4$ or $n_5$. However, $n_2$ and $n_3$ are exist in back bone. According to Jordan curve theorem, any successors of $p^\prime$ cannot reach a point $n_4$ or $n_5$ so this capability is inactive. Thus, a case of $t_{\pm 60}$ consumes some binding capabilities.

\item{Case of $t_{\pm 120}$}\\
  Binding capabilities that $p^\prime$ supply are inactive according to Jordan curve theorem on $n_1$ and $n_2$. Moreover, $p^\prime$ has to be bound to one of $n_3, n_4, n_5$ in order to deterministically stabilize.
Thus, a case of $t_{\pm 120}$ consumes some binging capabilities.

@@

            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};

@@

            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};

@@

            \node[transform canvas={shift=(0:1.2)},below] {$n_0$};
            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};

@@

Fig.\ref{TTT_tunnel_exit} exhibits all the two kings of exit of tunnel. 
At least one of point $n_1$ or $n_2$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.

@@

\begin{itemize}
\item{Case of $n_1$ and $n_2$ are free}\\
  This case can be regarded same situation as entrance. See Fig.\ref{TTT_tunnel_exit} (Left). Predecessor $n_5$ has to be bound $n_4$ and $n_5$ because each of $n_3$ and $n_4$ leave binding capabilities. Hence, at least $a=2$. This time, $\alpha = 2$ that is this case supply at most only $a$ binding capabilities.

\item{Case of $c$ is occupied}\\
  See Fig.\ref{TTT_tunnel_exit} (Right). If $n_1$ is occupied, then $n_2$ is free so that $n_5$ has to be bound $n_4$. Hence, at least $a=1$. This case can supply two binding capabilities but $p^\prime$ can bind to only one of $n_0$ or $n_2$ because $n_0$ or $n_2$ will be occupied a successor of $p^\prime$. Therefore, this case supply at most only $a=1$ active binding capability.

@@

\begin{itemize}
\item{Case of $n_1$ and $n_2$ are free}\\
  In $\alpha \geq 3$, if three neighbors of a bead leave, then it can supply two binding capabilities. Therefore Predecessor $n_5$ has to be bound $n_3$ and $n_4$, and $p^\prime$, too. In this case, at least consumes four bindings and supplies at most two bindings. Thus, it consumes some binding capabilities, totally.

\item{Case of $c$ is occupied}\\
  In this case, $n_4$ leave at least two bindings and $n_3$, $n_1$ also leave at least one binding. Therefore $n_5$ has to be bound $n_3$ and $n_4$, and $p^\prime$ also has to be bound $n_1$ and $n_4$. In this case, at least consumes four bindings and supplies at most one binding. Thus, it consumes some binding capabilities, totally.
\end{itemize}

@@

            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};

          \node at (0,-2) {Point $n_1$ and $n_2$ are free};
        \end{tikzpicture}
      \end{minipage}

@@

            \node[transform canvas={shift=(0:1.2)},right] {$n_0$};
            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};

          \node at (0,-2) {Point $n_1$ is occupied};
        \end{tikzpicture}
      \end{minipage}

@@

\begin{itemize}
\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
  In this figure, Bead $n_4$ has at least one binding so that $w[i-2]$ has to bound $n_4$. Moreover, $w[i-1]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically. On the other hand, $w[i]$ can supply two bindings but free neighbors of $w[i]$ are two points. One of them is occupied by a successor. Therefore $w[i]$ can only bind one of $n_5, n_6$ that is $w[i]$ supplies at most one binding. Thus, this case consumes some binding capabilities.

\item{Right of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
  This cases are divided on number of capabilities that $w[i-2]$ consumes.
  \begin{itemize}
  \item[-]{$w[i]$ does not consume any bindings}\\
    $w[i-1]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically. $w[i]$ has to be bound to $w[i-2]$ because $w[i-2]$ has bindings. This time, let us consider either $n_4$ is occupied or not. If $n_4$ is occupied, then $w[i-2]$ has no active bindings that is this situation consumes some binding capabilities. If $n_4$ is free and $w[i+1]$ is stabilized in $n_4$, then $w[i-2]$ has to bind $w[i+1]$. Therefore, In this case, stabilization of $w[i-2..i+1]$ consumes some bindings. If $n_4$ is free and $w[i+1]$ is stabilized except $n_4$, then this oritatami system has to use two binding capabilities in order to bind $w[i+1]$. Therefore, in this case consumes some bindings. Thus in this cases consume some binding capabilities.

  \item[-]{$w_i$ consumes one binding}\\
    In this case, $w_{i-1}$ has to be bound one of $n_1, n_2, n_3$. In addition, $w[i-2]$ and $w[i]$ are not supply any bindings. Thus, in this cases consume some binding capabilities.
  \item[-]{$w_i$ consumes two bindings}\\
    In this case, $w[i-2]$ already consumes two binding. $w[i-1]$ has to be bound. $w[i]$ supplies two bindings. Thus, in this cases consume some binding capabilities.

@@

          \node[left] at (-60:1.2) {$n_4$};

@@

            \foreach \theta in {120,60,-60,0}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

@@

            \node[below] at (180:1.2) {$w[i-2]$};
            \node[above] at (0:0) {$w[i-1]$};
            \node[right] at (-120:1.2) {$w[i]$};

            \node[left] at (120:1.2) {$n_3$};
            \node[left] at (60:1.2) {$n_2$};
            \node[left] at (0:1.2) {$n_1$};

@@

              \node[right] at (-120:1.2) {$n_5$};
              \node[right] at (-60:1.2) {$n_6$};
            \end{scope}

@@

            \node[below] at (180:1.2) {$w[i-2]$};
            \node[above] at (0:0) {$w[i-1]$};
            \node[right] at (-120:1.2) {$w[i]$};

            \node[left] at (120:1.2) {$n_3$};
            \node[left] at (60:1.2) {$n_2$};
            \node[left] at (0:1.2) {$n_1$};
